The Astropy Project

### 2017-10-20 main.tex
Update on Overleaf.

% Tom R: unit support description goes here and the sentence below is to be folded in with it.

Unit support in \texttt{modeling} has enabled implementation of the blackbody \citep{Rybicki1979} model, which requires units to make sense. It is available in \package{astropy} 2.0 as \texttt{BlackBody1D}.

@@

@@

\subsubsection{WCSAxes}

@@

This subpackage differs from APLpy \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas WCSAxes defines an interface that is much closer to that of Matplotlib \citep{matplotlib}, and makes it possible to make significantly more advanced visualizations.

@@

\citep{Lupton2004} describe an “optimal” algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays. The \package{visualization} package provides a convenience function to create such an image.  It also includes an associated set of classes to provide alternate scalings.
This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to Astropy from a more traditional engineering organization \citep{lsst_astropy}.

The SDSS SkyServer color images were made using a variation on this technique.
% Larry TODO:  include RGB image here

@@

\subsubsection{Lomb-Scargle Periodograms}
%jake

\subsubsection{Histogram Binning}
%jake

\section{Infrastructure for affiliated packages}
\label{sec:infrastructure}
\inlinecomment{BMS}{should we use links to the appropriate github repo?}
\inlinecomment{PLL}{IMHO a list of GitHub repo links for affil. pkgs. should be in appendix, if included.}
\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
%
\par In addition to astronomy related packages and libraries, the \astropy\
Project also contains and supports several infrastructure package that are
very generic. The following sections describes the most widely used
selection of them.
%
\subsection{Package template}
% Brigitta may write this up if there is no other takers
\par \astropy provides a template package that any \python package is welcome to
use (many affiliated packages do so). The template contains a ready-to-go
package layout. It provides infrastructure such as documentation tools,
testing framework and CI templates and configurations, Cython integration,
and documentation on how to make it all work.
%
\subsection{Continuous integration helpers}
% Brigitta
\package{ci-helpers} is a collection of scripts that empowers package
maintainers to control their testing set up and installation process for
various continuous integration services via a set of environment
variables. While the current development is mostly driven by the needs of
the \astropy ecosystem, the actual usage of this package is extremely
widespread. Currently we support setups for Travis CI and Appveyor CI.
%
\subsection{sphinx extensions}

% Tom R will work on this on Oct 18 and/or 19

>>>>

The \package{modeling} package now supports the representation, evaluation and fitting of models using \texttt{Quantity} objects, which attach units to scalar values or arrays of values. In practice, this means that one can for example fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluating it using input values with different but equivalent units. Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed fluxes in a variety of units and as a function of different units of spectral coordinates.

@@

\label{sec:stretch}

@@

\subsubsection{Plotting image data with world coordinates}

@@

This subpackage differs from APLpy \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas WCSAxes defines an interface that is much closer to that of Matplotlib \citep{matplotlib}, and makes it possible to make significantly more advanced visualizations. An example of a visualization made with \package{wcsaxes} is shown in Figure~\ref{fig:wcsaxes} -- this example illustrates the ability to overlay multiple coordinate systems and customize which ticks/labels are shown on which axes around the image. This also uses the image stretching functionality from Section~\ref{sec:stretch} to show the image in a square root stretch (automatically updating the tick positions in the colorbar).

\begin{figure}
\includegraphics[width=\textwidth]{cygnus_x_spitzer.pdf}
\caption{%
An example of figure made using the \package{visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0$\mu$m data from the Cygnus-X Spitzer Legacy survey \citep{cygnusx}.
\label{fig:wcsaxes}
}
\end{figure}

@@

\cite{Lupton2004} describe an “optimal” algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays. The \package{visualization} package provides a convenience function to create such a color image.  It also includes an associated set of classes to provide alternate scalings.
This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to Astropy from a more traditional engineering organization \citep{lsst_astropy}.

The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977} we show an RGB color image of the Hickson 88 group, centered near NGC~6977.  This image was generated from SDSS images using the \package{astropy.visualization} tools.

\begin{figure}
\includegraphics[width=\textwidth]{ngc6977.png}
\caption{An RGB color image of the region near the Hickson 88 group
constructed from SDSS images and the \package{astropy.visualization}
tools.
\label{fig:ngc6977}}
\end{figure}

@@

\subsubsection{Lomb-Scargle Periodograms}
Periodic analysis of unevenly-spaced time series is common across subfields of Astronomy. The \package{stats} package includes several efficient implementations of the Lomb-Scargle periodogram \citep{Lomb76, Scargle82} and several generalizations, floating mean models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003}, and appropriate handling of heteroscedastic uncertainties. Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.][]{Press89, Palmer09}, and so can be applied to much larger datasets than algorithms available in, e.g. \package{scipy.stats} (\citealt{scipy}). Much of the Lomb-Scargle code in AstroPy has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.

\subsubsection{Bayesian Blocks and Histogram Binning}
AstroPy also includes an implementation of {\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of break-points in non-periodic astronomical time-series. One interesting application of Bayesian Blocks is its use in determining optimal histogram binnings, and in particular binnings with unequal bin sizes. This code was adapted, with several improvements, from the \package{astroML} package \citep{astroML}.

\inlinecomment{JTV}{Should we include an example BB histogram from the astropy docs?}

\section{Infrastructure for affiliated packages}
\label{sec:infrastructure}
\inlinecomment{BMS}{should we use links to the appropriate github repo?}
\inlinecomment{PLL}{IMHO a list of GitHub repo links for affil. pkgs. should be in appendix, if included.}
\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
%
\par In addition to astronomy related packages and libraries, the \astropy\
Project also contains and supports several infrastructure package that are
very generic. The following sections describes the most widely used
selection of them.
%
\subsection{Package template}
% Brigitta may write this up if there is no other takers
\par \astropy provides a template package that any \python package is welcome to
use (many affiliated packages do so). The template contains a ready-to-go
package layout. It provides infrastructure such as documentation tools,
testing framework and CI templates and configurations, Cython integration,
and documentation on how to make it all work.
%
\subsection{Continuous integration helpers}
% Brigitta
\package{ci-helpers} is a collection of scripts that empowers package
maintainers to control their testing set up and installation process for
various continuous integration services via a set of environment
variables. While the current development is mostly driven by the needs of
the \astropy ecosystem, the actual usage of this package is extremely
widespread. Currently we support setups for Travis CI and Appveyor CI.
%
\subsection{Sphinx extensions}

The documentation for many Python packages the core \package{astropy} package as well as for all packages in the Astropy ecosystem is written using the Sphinx package. This package makes it possible to write the documentation using plain text files that follow a markup language called reStructuredText, and Sphinx can then transform this into HTML or \LaTeX documentation. As part of the project, we have developed a few extensions that facilitate generating documentation for a large project like Astropy. One of the main extensions we have developed is \package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}}, which makes it easy with a single reStructuredText command to generate a set of documentation pages listing all the available classes, functions, and attributes in any given Python module.

\inlinecomment{TPR}{We should put the releases of sphinx-automodapi on Zenodo and cite this}

% TODO: need to put releases of sphinx-automodapi on Zenodo!
